Action alternatives & confidence factor

### 2023-08-10 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/action_alternatives_confidence_factor.Rmd
Update action_alternatives_confidence_factor.Rmd

library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl, 
      gridExtra,
      janitor,
      RColorBrewer,
      cowplot,
      zoo)

@@

```{r}
# novices: correlation between confidence factor and count
main %>% 
  filter(id %in% c("Novice")) -> corr.nov

>>>>

library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl, 
      gridExtra,
      janitor,
      RColorBrewer,
      cowplot,
      zoo,
      apaTables)

@@

```{r}

# Korrelationstabelle nach APA-Standards

head(main)

# Subset anlegen nur mit Variablen
main %>% 
  select(confidence_factor, 
         count, 
         nd,
         percent_nd) -> corr_subset

apa.cor.table(corr_subset, filename = "Korrelationen.doc")

# novices: correlation between confidence factor and count
main %>% 
  filter(id %in% c("Novice")) -> corr.nov
